### 2018-12-04 tex/paper.tex
Including appendix.

%==> Stereo_special_mf_1.640000_12.990000_50.840000_1.510000_1.100000/cones_left_mf_1.640000_12.990000_50.840000_1.510000_1.100000.txt <==
%239.143 2.67669e+07
%
%==> Stereo_special_mf_1.640000_12.990000_50.840000_1.510000_1.100000/teddy_left_mf_1.640000_12.990000_50.840000_1.510000_1.100000.txt <==
%555.304 2.35632e+07
%
%==> Stereo_special_mf_1.640000_12.990000_50.840000_1.510000_1.100000/tsukuba_left_mf_1.640000_12.990000_50.840000_1.510000_1.100000.txt <==
%14.9264 8.21469e+06
%
%==> Stereo_special_mf_1.640000_12.990000_50.840000_1.510000_1.100000/venus_left_mf_1.640000_12.990000_50.840000_1.510000_1.100000.txt <==
%60.3171 1.83186e+07
%
%==> Stereo_special_submod_1.640000_12.990000_50.840000_1.510000_1.100000/cones_left_submod_1.640000_12.990000_50.840000_1.510000_1.100000.txt <==
%1082.72 1.26817e+07
%
%==> Stereo_special_submod_1.640000_12.990000_50.840000_1.510000_1.100000/teddy_left_submod_1.640000_12.990000_50.840000_1.510000_1.100000.txt <==
%1257.86 1.57924e+07
%
%==> Stereo_special_submod_1.640000_12.990000_50.840000_1.510000_1.100000/tsukuba_left_submod_1.640000_12.990000_50.840000_1.510000_1.100000.txt <==
%215.219 4.12202e+06
%
%==> Stereo_special_submod_1.640000_12.990000_50.840000_1.510000_1.100000/venus_left_submod_1.640000_12.990000_50.840000_1.510000_1.100000.txt <==
%469.752 1.55122e+07
%\begin{minipage}
%\end{minipage}

@@

\myparagraph{Results}

Figure \ref{fig:stereo} shows some example solutions obtained by picking the
label with maximum marginal probability for each variable for mean-field and
for our algorithm. We also report the time and energy values of the solution
for both methods. Though we are not performing MAP estimation, energy values
give us a quantitative indication of the quality of solutions. For the full set of
21 image pairs (2006 dataset), the average ratio of the energies of the solutions from our method 
compared to mean-field is 0.943. The avearge time ratio is 10.66. We observe that our algorithm results in more natural looking stereo matching results with lower energy values for all images. However, mean-field runs faster than our method for each instance.

>>>>

@@

\myparagraph{Results} Figure \ref{fig:stereo} shows some example solutions obtained by picking the
label with maximum marginal probability for each variable for mean-field and
for our algorithm. We also report the time and energy values of the solution
for both methods. Though we are not performing MAP estimation, energy values
give us a quantitative indication of the quality of solutions. For the full set of
21 image pairs (2006 dataset), the average ratio of the energies of the solutions from our method 
compared to mean-field is 0.943. The avearge time ratio is 10.66. We observe that our algorithm results in more natural looking stereo matching results with lower energy values for all images. However, mean-field runs faster than our method for each instance.

\mysubsection{Stereo Matching using Higher-order Potts Model}
\label{subsec:stereo_hop}
\myparagraph{Data} Next, we use the higher-order Potts model for stereo
matching on the Middlebury dataset. For this
purpose, we take a dense CRF model with Potts compatibility term and Gaussian pairwise
potentials, and augment it with higher-order Potts term.

\myparagraph{Method} We again use the modified Gaussian filtering implementation for dense CRFs by
\citep{ajanthan2017efficient} to compute the conditional gradient at each step.
To compute the contribution of the higher-order Potts, we make use of an
efficient strategy to reuse computation. Recall that computing the conditional
gradient coordinates $s^*_{\sigma(i)}$ requires us to obtain differences of the
nested sets $F(S_i) - F(S_{i - 1})$. We store the clique state at each $i$, and
this enables us to compute the difference for each coordinate in a constant
amount of time. In this case, computation of conditional gradient takes
$\mathcal{O}(cNL)$ where $c$ is the number of hihger-order cliques.

\myparagraph{Results} Figure \ref{fig:stereo_hop} shows some example solutions obtained by picking the
label with maximum marginal probability for each variable.
